### 2019-06-06 2-Chapters/1-Chapter/chapter1.tex
Changed \paragraph{XXX} to \paragraph{XXX.}
Fixed the Nomenclature

\begin{figure}[h!]
    \centering
    % \resizebox{1.00\textwidth}{!}{
    \begin{tikzpicture}[>=latex',line join=bevel,scale=2.25]
        %
        \node[align=center] (introduction) at (0,3.25) [rectangle,draw] {Chapter~\ref{chapter:1}\\Introduction};
        \node[align=center] (chapter2) at (0,2.25) [rectangle,draw] {Chapter~\ref{chapter:2}\\Stochastic and Stationary\\Multi-Armed Bandit models};
        \node[align=center] (chapter3) at (2.5,2.25) [rectangle,draw] {Chapter~\ref{chapter:3}\\SMPyBandits: simulation\\library for MAB};
        \node[align=center] (chapter4) at (-2.5,1) [rectangle,draw] {Chapter~\ref{chapter:4}\\Two MAB models\\for IoT networks};
        \node[align=center] (chapter5) at (0,1) [rectangle,draw] {Chapter~\ref{chapter:5}\\Multi-players\\MAB models};
        \node[align=center] (chapter6) at (2.5,1) [rectangle,draw] {Chapter~\ref{chapter:6}\\Non-stationary\\MAB models};
        \node[align=center] (conclusion) at (0,-0.25) [rectangle,draw] {Chapter~\ref{chapter:conclusion}\\General conclusion};
        %
        \draw [color=black,thick,->] (introduction) to (chapter2);
        \draw [color=black,thick,<->] (chapter2) to (chapter3);
        \draw [color=black,thick,->] (chapter2) to (chapter4);
        \draw [color=black,thick,->] (chapter2) to (chapter5);
        \draw [color=black,densely dotted,<->]   (chapter4) to (chapter5);
        \draw [color=black,densely dotted,->] -| (chapter3) to (chapter6);
        \draw [color=black,densely dotted,<->]   (chapter5) to (chapter6);
        \draw [color=black,thick,->] (chapter2) to (chapter6);
        \draw [color=black,thick,->] (chapter4) to (conclusion);
        \draw [color=black,thick,->] (chapter5) to (conclusion);
        \draw [color=black,thick,->] (chapter6) to (conclusion);
        %
    \end{tikzpicture}
    % }
    \caption{Organization of the thesis: a reading map. Any path containing Chapter~\ref{chapter:1}, Chapter~\ref{chapter:2}, at least one of the three Chapters~\ref{chapter:4}, \ref{chapter:5} and \ref{chapter:6}, and the Conclusion is a self contained way to read this thesis.}
    \label{fig:1:organization}
\end{figure}

@@

\item
    \emph{GNU Radio Implementation of MALIN: ``Multi-Armed bandits Learning for Internet-of-things Networks''},
    by \textbf{Lilian Besson}, Rémi Bonnefoi \& Christophe Moy.
    \emph{Wireless Communication and Networks Conference}\footnote{~IEEE WCNC 2019, see \href{http://wcnc2019.ieee-wcnc.org}{\texttt{wcnc2019.ieee-wcnc.org}}}, Marrakech, Morocco, April 2019,
    \href{https://HAL.Inria.fr/hal-02006825}{\texttt{HAL.Inria.fr/hal-02006825}}.
    \cite{Besson2019WCNC}

@@

\item
    \emph{Aggregation of Multi-Armed Bandits learning algorithms for Opportunistic Spectrum Access},\\
    by \textbf{Lilian Besson}, Emilie Kaufmann \& Christophe Moy.
    \emph{Wireless Communication and Networks Conference}\footnote{~IEEE WCNC 2018, see \href{http://wcnc2018.ieee-wcnc.org}{\texttt{wcnc2018.ieee-wcnc.org}}}, Barcelone, Spain, April 2018,
    \href{https://HAL.Inria.fr/hal-01705292}{\texttt{HAL.Inria.fr/hal-01705292}}.
    \cite{Besson2018WCNC}

@@

\item
    \emph{SMPyBandits: an Open-Source Research Framework for Single and Multi-Players Multi-Arms Bandits (MAB) Algorithms in Python},
    by \textbf{Lilian Besson}, active development since October $2016$,
    \href{https://HAL.Inria.fr/hal-01840022}{\texttt{HAL.Inria.fr/hal-01840022}}.
    About $40000$ lines of code, hosted on \href{https://GitHub.com/SMPyBandits}{\texttt{GitHub.com/SMPyBandits}},
    and documentation on \href{https://SMPyBandits.rtfd.io}{\texttt{SMPyBandits.rtfd.io}}.
    \cite{SMPyBandits,SMPyBanditsJMLR}

\item
    \emph{What Doubling-Trick Can and Can't Do for Multi-Armed Bandits},
    by \textbf{Lilian Besson} \& Emilie Kaufmann,
    September $2018$,\\
    \href{https://HAL.Inria.fr/hal-01736357}{\texttt{HAL.Inria.fr/hal-01736357}}.
    \cite{Besson2018DoublingTricks}

>>>>

\begin{figure}[h!]
    \centering
    % \resizebox{1.00\textwidth}{!}{
    \begin{tikzpicture}[>=latex',line join=bevel,scale=2.25]
        %
        \node[align=center] (introduction) at (0,3.25) [rectangle,draw] {Chapter~\ref{chapter:1}\\Introduction};
        \node[align=center] (chapter2) at (0,2.25) [rectangle,draw] {Chapter~\ref{chapter:2}\\Stochastic and Stationary\\Multi-Armed Bandit models};
        \node[align=center] (chapter3) at (2.5,2.25) [rectangle,draw] {Chapter~\ref{chapter:3}\\SMPyBandits: simulation\\library for MAB};
        \node[align=center] (chapter4) at (-2.5,1) [rectangle,draw] {Chapter~\ref{chapter:4}\\Two MAB models\\for IoT networks};
        \node[align=center] (chapter5) at (0,1) [rectangle,draw] {Chapter~\ref{chapter:5}\\Multi-players\\MAB models};
        \node[align=center] (chapter6) at (2.5,1) [rectangle,draw] {Chapter~\ref{chapter:6}\\Non-stationary\\MAB models};
        \node[align=center] (conclusion) at (0,-0.25) [rectangle,draw] {Chapter~\ref{chapter:conclusion}\\General conclusion};
        %
        \draw [color=black,thick,->] (introduction) to (chapter2);
        \draw [color=black,thick,<->] (chapter2) to (chapter3);
        \draw [color=black,thick,->] (chapter2) to (chapter4);
        \draw [color=black,thick,->] (chapter2) to (chapter5);
        \draw [color=black,densely dotted,<->]   (chapter4) to (chapter5);
        \draw [color=black,densely dotted,->] -| (chapter3) to (chapter6);
        \draw [color=black,densely dotted,<->]   (chapter5) to (chapter6);
        \draw [color=black,thick,->] (chapter2) to (chapter6);
        \draw [color=black,thick,->] (chapter4) to (conclusion);
        \draw [color=black,thick,->] (chapter5) to (conclusion);
        \draw [color=black,thick,->] (chapter6) to (conclusion);
        %
    \end{tikzpicture}
    % }
    \caption[Organization of the thesis: a reading map]{Organization of the thesis: a reading map. Any path containing Chapter~\ref{chapter:1}, Chapter~\ref{chapter:2}, at least one of the three Chapters~\ref{chapter:4}, \ref{chapter:5} and \ref{chapter:6}, and the Conclusion is a self contained way to read this thesis.}
    \label{fig:1:organization}
\end{figure}

@@

\item
    \emph{GNU Radio Implementation of MALIN: ``Multi-Armed bandits Learning for Internet-of-things Networks''},
    by \textbf{Lilian Besson}, Rémi Bonnefoi \& Christophe Moy.
    \emph{Wireless Communication and Networks Conference}\footnote{~IEEE WCNC 2019, see \href{http://wcnc2019.ieee-wcnc.org}{\texttt{wcnc2019.ieee-wcnc.org}}}, Marrakech, Morocco, April 2019,\\
    \href{https://HAL.Inria.fr/hal-02006825}{\texttt{HAL.Inria.fr/hal-02006825}}.
    \cite{Besson2019WCNC}

@@

\item
    \emph{Aggregation of Multi-Armed Bandits learning algorithms for Opportunistic Spectrum Access},\\
    by \textbf{Lilian Besson}, Emilie Kaufmann \& Christophe Moy.
    \emph{Wireless Communication and Networks Conference}\footnote{~IEEE WCNC 2018, see \href{http://wcnc2018.ieee-wcnc.org}{\texttt{wcnc2018.ieee-wcnc.org}}}, Barcelone, Spain, April 2018,\\
    \href{https://HAL.Inria.fr/hal-01705292}{\texttt{HAL.Inria.fr/hal-01705292}}.
    \cite{Besson2018WCNC}

@@

\item
    \emph{SMPyBandits: an Open-Source Research Framework for Single and Multi-Players Multi-Arms Bandits (MAB) Algorithms in Python},
    by \textbf{Lilian Besson}, active development since October $2016$,
    \href{https://HAL.Inria.fr/hal-01840022}{\texttt{HAL.Inria.fr/hal-01840022}}.\\
    About $40000$ lines of code, hosted on \href{https://GitHub.com/SMPyBandits}{\texttt{GitHub.com/SMPyBandits}},
    and documentation on \href{https://SMPyBandits.rtfd.io}{\texttt{SMPyBandits.rtfd.io}}.
    \cite{SMPyBandits,SMPyBanditsJMLR}

\item
    \emph{What Doubling-Trick Can and Can't Do for Multi-Armed Bandits},
    by \textbf{Lilian Besson} \& Emilie Kaufmann,
    September $2018$,
    \href{https://HAL.Inria.fr/hal-01736357}{\texttt{HAL.Inria.fr/hal-01736357}}.
    \cite{Besson2018DoublingTricks}

### 2019-06-06 5-Nomenclature/Nomenclature.tex
Working to merge Christophe's feedback of Chapter5
Fixed the Nomenclature

% Algorithms or tools
\nomenclature[A]{UCB}{\textit{Upper Confidence Bound} (object or algorithm)}
\nomenclature[A]{klUCB}{\textit{Kullback-Leibler Upper Confidence Bound} (algorithm)}
\nomenclature[A]{TS}{\textit{Thompson Sampling} (algorithm)}
\nomenclature[A]{KL}{\textit{Kullback-Leibler} (divergence)}
\nomenclature[A]{MCTopM}{\textit{Musical-Chair on Top-M} (algorithm)}
\nomenclature[A]{RandTopM}{\textit{Random Hoping on Top-M} (algorithm)}
\nomenclature[A]{GLR}{\textit{Generalized Likelihood Ratio}}
\nomenclature[A]{MAB}{\textit{Multi-Armed Bandit}}
\nomenclature[A]{ML}{\textit{Machine Learning}}
\nomenclature[A]{RL}{\textit{Reinforcement Learning}}
\nomenclature[A]{GLRT}{\textit{Generalized Likelihood Ratio Test}}

% --------------------------------
% matches Greek Symbols        > G
\nomenclature[G]{$\nu_k$, $\nu_k(t)$, $\nu_k^j$}{Distribution of arm $k$, arm $k$ at time $t$, arm $k$ for user $j$}
\nomenclature[G]{$\mu_k$, $\mu_k(t)$, $\mu_k^j$, $\mu_i^{(k)}$}{Mean of arm $k$, arm $k$ at time $t$, arm $k$ for user $j$ in Chapter~\ref{chapter:5}, arm $i$ in the $k$-th stationary interval in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\mu^*$, $\mu_k^*$}{Mean of the optimal arm (\ie, $\mu^*=\max_k \mu_k$), and mean of the $k$-th best arm}
\nomenclature[G]{$\bm{\mu},\bm{\nu},\bm{\lambda},$}{Vector of means $(\mu_k) = \mu_1,\dots,\mu_K$, or vector of distributions $(\nu_k)_k$ or $(\lambda_k)_k$ (characterizing a problem)}
\nomenclature[G]{$\Delta$}{Usually denotes the gap in terms of means of arms, usually between the best and second best arms, in Chapters~\ref{chapter:2}, \ref{chapter:5}. In Chapter~\ref{chapter:4} in Algorithm~\ref{algo:43:UCBwithDelay} it denotes a delay. In Chapter~\ref{chapter:6}, it can denote different gaps}
\nomenclature[G]{$\Delta n$, $\Delta s$}{Parameters of numerical optimization tricks in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\delta$}{Usually denotes a lower-bound on the gap $\Delta$, known before hand by an algorithm, in Chapters~\ref{chapter:5}, \ref{chapter:6}. Also denote a confidence level of an algorithm in Section~\ref{sec:6:ChangePointDetector}}
\nomenclature[G]{$\Upsilon_T$}{Number of break-points in a piece-wise stationary MAB problem in Chapter~\ref{chapter:6}. $\NCi$ denotes the number of change-points on arm $i$, and $C_T = \sum_{i=1}^{K} \NCi$ the number of change-points on the arms}
\nomenclature[G]{$\tau_k^j$, $\tau^{(k)}$}{Usually denotes the location of a change-point, \eg, the $j$-th change-point on arm $k$, in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\tau$}{Usually denotes the length of a sliding-window, \eg, in SW-\UCB{} in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\gamma$}{Usually denotes a discount factor, \eg, in D-\UCB{} or D-TS in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\varepsilon$}{Usually denotes a small positive real value, \eg, $\lambda_k = \mu_k + \varepsilon$ in Chapter~\ref{chapter:5} or a drift correction parameter in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\alpha$}{Usually denotes the parameter of a \UCB{} algorithm in Chapters~\ref{chapter:2} and \ref{chapter:4}, or a parameter controlling the forced exploration mechanism in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\beta$}{Usually denotes a threshold of GLR tests in Chapter~\ref{chapter:6}}

\nomenclature[G]{$\alpha_0$, $\delta_0$}{Usually denotes a constant scaling of a parameter of an algorithm, for instance $\alpha = \alpha_0 \alpha_T$ is used in Chapter~\ref{chapter:6}, where $\alpha_T$ is the formula suggested by the theoretical analysis and $\alpha_0 > 0$, \eg, $\alpha_0 = 0.01$}

% --------------------------------
% matches Roman Symbols        > L
\nomenclature[L]{$t$, $s$, $n$, $r$}{Time step, $t\in\{1,\dots,T\}$. Chapter~\ref{chapter:6} also uses $s$, $n$ and $r$, \eg, in the $\sup$ of the stopping times or some technical lemmas}
\nomenclature[L]{$T$}{Time horizon, the duration of the bandit game (always $T\geq1$)}
\nomenclature[L]{$T_0$, $T_1$}{Fixed durations of some algorithms based on different phases, \eg, the Musical Chair algorithm from \cite{Rosenski16}}
\nomenclature[L]{$\cA$, $\pi$}{A algorithm, a policy, designing the algorithm (\eg, \UCB) rather than the strategy. $\pi$ can also denote a permutation in Section~\ref{par:5:twoIdeasOrthogonalization}}
\nomenclature[L]{$\rho$, $\rho^k$}{A bandit strategy, denoting the mathematical object which maps past observations to future decisions (mainly in Chapter~\ref{chapter:5})}
\nomenclature[L]{$A(t)$, $A^j(t)$}{Decision of algorithm $\cA$ at time $t$, $A(t)\in\{1,\dots,K\}$. Decision for user $j$ in Chapter~\ref{chapter:5}}
\nomenclature[L]{$Y_{k,t}$}{Random sample from the arm $k$ at time $t$}
\nomenclature[L]{$\cO_t$}{Vector of observations until time $t$ in Chapter~\ref{chapter:5}}
\nomenclature[L]{$r(t)$, $r^j(t)$}{Reward obtained at time $t$, for user $j$ at time $t$}
\nomenclature[L]{$K$}{Number of arms for multi-armed bandit games}
\nomenclature[L]{$k$}{Usually denotes the $k$-th arm, $k\in\{1,\dots,K\}$, mainly used in subscripts}
\nomenclature[L]{$M$}{In Chapter~\ref{chapter:4}, denote the maximum number of retransmission of a packet in the ALOHA protocol, and in Chapter~\ref{chapter:5}, denote the number of player for multi-players bandit games}
\nomenclature[L]{$m$}{In Chapter~\ref{chapter:4}, denote the maximum length of the back-off interval after a collision}
\nomenclature[L]{$i$, $j$}{Usually denotes the $i$-th or $j$-th player, $i,j\in\{1,\dots,M\}$ in Chapter~\ref{chapter:5}}
\nomenclature[L]{$N$}{Usually denotes the number of independent repetitions of the same numerical experiments (\eg, $N=1000$). In Chapter~\ref{chapter:4}, denote the number of IoT (dynamic) devices in the studied network}

@@

\nomenclature[L]{$C_k(t)$, $C^j(t)$}{In Chapters~\ref{chapter:4} and \ref{chapter:5}, collision indicator on arm $k$ or for user $j$ at time $j$}

\nomenclature[L]{$C_{\bm{\mu}}$, $D_{\bm{\mu}}$, $G_{M,\bm{\mu}}$}{In Chapter~\ref{chapter:5}, constants depending on the problem parameters only (or also on $M$)}

@@

\nomenclature[O]{$\Pr$}{Probability measure under a probabilistic model}
\nomenclature[O]{$\E$}{Expectancy under a probabilistic model}
\nomenclature[O]{$\mathbbm{1}(E)$}{Indicator function of an event $E$ ($= 1$ if and only if the event $E$ is true)}
\nomenclature[O]{$\cF$, $\cF_t$}{Filtration in a probabilistic model, after $t-1$ prior observations}
\nomenclature[O]{$[K]$, $[N]$ etc}{For an integer $N\in\N$, $N\geq0$, $[N]$ denotes the set $\{1,\dots,N\}$. If the order is important, it is ordered from $1$ to $N$.}
% \nomenclature[O]{$I_1,\dots,I_5$}{Used in Chapter~\ref{chapter:5} to denote various events}
\nomenclature[O]{$\cE$, $\cE_T$}{Used in Chapter~\ref{chapter:6} to denote ``good events'' that happen most of the time}

\nomenclature[O]{$\lfloor \bullet \rfloor$, $\lceil \bullet \rceil$}{Floor and ceiling funtions, $\lfloor x \rfloor = \sup\{n\in\Z, x \leq n\}$ and $\lceil x \rceil = \sup\{n\in\Z, x < n\}$}

@@

% --------------------------------
% matches Subscripts           > I
\nomenclature[I]{$x_k$}{Usually denotes a variable depending on an arm, for $k\in\{1,\dots,K\}$}

% --------------------------------
% matches Superscripts         > E
\nomenclature[E]{$y^j$}{Usually denotes a variable depending on a player, for $j\in\{1,\dots,M\}$}
\nomenclature[E]{$y^{(k)}$, $y^{(\ell)}$}{Usually the superscript index $(k)$ (resp. $(\ell)$) denotes a variable in the $k$-th stationary interval, under the \emph{global} (resp. \emph{local}) changes point-of-view, in Chapter~\ref{chapter:6}}

>>>>

% Algorithms or tools
\nomenclature[A]{UCB}{\textit{Upper Confidence Bound} (object or algorithm)}
\nomenclature[A]{klUCB}{\textit{Kullback-Leibler Upper Confidence Bound} (algorithm)}
\nomenclature[A]{TS}{\textit{Thompson Sampling} (algorithm)}
\nomenclature[A]{KL}{\textit{Kullback-Leibler} (divergence)}
\nomenclature[A]{MCTopM}{\textit{Musical-Chair on Top-M} (algorithm)}
\nomenclature[A]{RandTopM}{\textit{Random Hoping on Top-M} (algorithm)}
\nomenclature[A]{GLR, GLRT}{\textit{Generalized Likelihood Ratio}, \textit{Generalized Likelihood Ratio Test}}
\nomenclature[A]{MAB}{\textit{Multi-Armed Bandit}}
\nomenclature[A]{ML}{\textit{Machine Learning}}
\nomenclature[A]{RL}{\textit{Reinforcement Learning}}

% --------------------------------
% matches Greek Symbols        > G
\nomenclature[G]{$\nu_k$, $\nu_k(t)$, $\nu_k^j$}{Distribution of arm $k$, arm $k$ at time $t$, arm $k$ for user $j$}
\nomenclature[G]{$\mu_k$, $\mu_k(t)$, $\mu_k^j$, $\mu_i^{(k)}$}{Mean of arm $k$, arm $k$ at time $t$ (in Chapter~\ref{chapter:6}), arm $k$ for user $j$ (in Chapter~\ref{chapter:5}), arm $i$ in the $k$-th stationary interval (in Chapter~\ref{chapter:6})}
\nomenclature[G]{$\mu^*$, $\mu_k^*$}{Mean of the optimal arm (\ie, $\mu^*=\max_k \mu_k$), and mean of the $k$-th best arm}
\nomenclature[G]{$\bm{\mu},\bm{\nu},\bm{\lambda},$}{Vector of means $(\mu_k) = \mu_1,\dots,\mu_K$, or vector of distributions $(\nu_k)_k$ or $(\lambda_k)_k$ (characterizing a problem)}
\nomenclature[G]{$\Delta$}{Usually denotes the gap in terms of means of arms, usually between the best and second best arms, in Chapters~\ref{chapter:2}, \ref{chapter:5}. In Chapter~\ref{chapter:4} in Algorithm~\ref{algo:43:UCBwithDelay} it denotes a delay. In Chapter~\ref{chapter:6}, it can denote different gaps ($\Delta^{\text{opt}}$ and $\Delta^{\text{change}}$)}
\nomenclature[G]{$\Delta n$, $\Delta s$}{Parameters of numerical optimization tricks in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\delta$}{Usually denotes a lower-bound on the gap $\Delta$, known before hand by an algorithm, in Chapters~\ref{chapter:5}, \ref{chapter:6}. Also denote a confidence level of an algorithm in Section~\ref{sec:6:ChangePointDetector}}
\nomenclature[G]{$\Upsilon_T$}{Number of break-points in a piece-wise stationary MAB problem in Chapter~\ref{chapter:6}. $\NCi$ denotes the number of change-points on arm $i$, and $C_T = \sum_{i=1}^{K} \NCi$ the number of change-points on the arms}
\nomenclature[G]{$\tau_k^j$, $\tau^{(k)}$}{Location of a change-point, \eg, the $j$-th change-point on arm $k$, in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\tau$}{Length of a sliding-window, \eg, in SW-\UCB{} in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\gamma$}{Usually denotes a discount factor, \eg, in D-\UCB{} or D-TS in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\varepsilon$}{Usually denotes a small positive real value, \eg, the parameter for the $\varepsilon$-greedy algorithm, or a drift correction parameter for the \CUSUM{} algorithm in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\alpha$}{Usually denotes the parameter of a \UCB{} algorithm in Chapters~\ref{chapter:2} and \ref{chapter:4}, or a parameter controlling the forced exploration mechanism in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\beta(n,\delta)$}{Usually denotes a threshold for the statistical (GLR) tests in Chapter~\ref{chapter:6}}

\nomenclature[G]{$\alpha_0$, $\delta_0$}{Usually denotes a constant scaling of a parameter of an algorithm, for instance $\varepsilon_t = \varepsilon_0 / t$ is used in Chapter~\ref{chapter:2}, or $\alpha = \alpha_0 \alpha_T$ is used in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\pi$}{It usually denotes the number $\pi\simeq 3.14\ldots$, but it also denotes a probability distribution in Section~\ref{sec:2:chooseYourPreferredBanditAlgorithm} or a permutation in Section~\ref{par:5:twoIdeasOrthogonalization}}
% \nomenclature[G]{$\rho$, $\rho^k$}{A bandit strategy, denoting the mathematical object which maps past observations to future decisions (mainly in Chapter~\ref{chapter:5})}

% --------------------------------
% matches Roman Symbols        > L
\nomenclature[L]{$t$, $s$, $n$, $r$}{Time step, $t\in[T]$. Chapter~\ref{chapter:6} also uses $s$, $n$ and $r$, \eg, in the $\sup$ of the stopping times or some technical lemmas}
\nomenclature[L]{$T$}{Time horizon, the duration of the bandit game (always $T\geq1$)}
\nomenclature[L]{$T_0$, $T_1$}{Fixed durations of some algorithms based on different phases, \eg, the Musical Chair algorithm from \cite{Rosenski16}}
\nomenclature[L]{$\cA$}{An algorithm, also referred to as a policy or a strategy. $\cA_1,\dots,\cA_N$ denote the $N$ aggregated algorithms in Section~\ref{sec:2:chooseYourPreferredBanditAlgorithm} and $\cA_1,\dots,\cA_M$ denotes the algorithms of the $M$ players in Chapter~\ref{chapter:5}}
\nomenclature[L]{$A(t)$, $A^j(t)$}{Decision of algorithm $\cA$ at time $t\in[T]$, $A(t)\in[K]$ (from algorithm $\cA$), decision for user $j\in[M]$ in Chapter~\ref{chapter:5} (from algorithm $\cA^j$)}
\nomenclature[L]{$Y_{k,t}$}{Random sample from the arm $k$ at time $t$}
\nomenclature[L]{$\cO_t$}{Vector of observations until time $t$ in Chapter~\ref{chapter:5}}
\nomenclature[L]{$r(t)$, $r^j(t)$}{Reward obtained at time $t$, for user $j$ at time $t$}
\nomenclature[L]{$K$}{Number of arms for multi-armed bandit games}
% \nomenclature[L]{$[T}$, $[K]$, etc}{The set of integers from $1$ to $T$, $[T]=\{1,\dots,T\} = \{ n \in\N: 1 \leq n \leq T\}$}
\nomenclature[L]{$k$}{Usually denotes the $k$-th arm, $k\in[K]$, mainly used in subscripts}
\nomenclature[L]{$M$}{In Chapter~\ref{chapter:4}, denote the maximum number of retransmission of a packet in the ALOHA protocol, and in Chapter~\ref{chapter:5}, denote the number of player for multi-players bandit games}
\nomenclature[L]{$m$}{In Chapter~\ref{chapter:4}, denote the maximum length of the back-off interval after a collision}
\nomenclature[L]{$i$, $j$}{Usually denotes the $i$-th or $j$-th player, $i,j\in[M]$ in Chapter~\ref{chapter:5}}
\nomenclature[L]{$N$}{Usually denotes the number of independent repetitions of the same numerical experiments (\eg, $N=1000$). In Chapter~\ref{chapter:4}, denote the number of IoT (dynamic) devices in the studied network}

@@

\nomenclature[L]{$C_k(t)$, $C^j(t)$}{In Chapters~\ref{chapter:4} and \ref{chapter:5}, collision indicator, on arm $k\in[K]$ or for user $j\in[M]$, at time $j$}

\nomenclature[L]{$C_{\bm{\mu}}$, $D_{\bm{\mu}}$, $G_{M,\bm{\mu}}$}{In Chapter~\ref{chapter:5}, constants depending on the problem parameters only and on $M$}

@@

\nomenclature[O]{$\Pr$}{Probability measure under a probabilistic model}
\nomenclature[O]{$\E$}{Expectancy under a probabilistic model}
\nomenclature[O]{$\mathbbm{1}(E)$}{Indicator function of an event $E$ ($= 1$ if and only if the event $E$ is true)}
\nomenclature[O]{$\cF$, $\cF_t$}{Filtration in a probabilistic model, after $t-1$ prior observations}
\nomenclature[O]{$[K]$, $T$, $[N]$ etc}{For an integer $N\in\N$, $N\geq0$, $[N]$ denotes the set $\{1,\dots,N\} = \{ n \in\N : 1 \leq n \leq N \}$. If the order is important, it is ordered from $1$ to $N$.}
% \nomenclature[O]{$I_1,\dots,I_5$}{Used in Chapter~\ref{chapter:5} to denote various events}
\nomenclature[O]{$\cE$, $\cE_T$}{Used in Chapter~\ref{chapter:6} to denote ``good events'' that happen most of the time}

\nomenclature[O]{$\lfloor \bullet \rfloor$, $\lceil \bullet \rceil$}{Floor $\lfloor x \rfloor = \sup\{n\in\Z, n \leq x\}$ and ceil $\lceil x \rceil = \inf\{n\in\Z, x < n\}$ functions}

@@

% --------------------------------
% matches Subscripts           > I
\nomenclature[I]{$x_k$}{Usually denotes a variable depending on an arm, for $k\in[K]$}
\nomenclature[I]{$Y_{k,t}$}{Usually denotes a variable depending on an arm, for $k\in[K]$, and on time, for $t\in[T]$}

% --------------------------------
% matches Superscripts         > E
\nomenclature[E]{$y^j$}{Usually denotes a variable depending on a player in Chapter~\ref{chapter:5} (for $j\in[M]$), or to distinguish between different independent runs in numerical simulations in Chapter~\ref{chapter:2} (for $j\in[N]$)}
\nomenclature[E]{$y^{(k)}$, $y^{(\ell)}$}{Usually the superscript index $(k)$ or $(\ell)$ denotes a variable in the $k$-th stationary interval, under the  point-of-views of \emph{global} or \emph{local} changes, in Chapter~\ref{chapter:6}}
